SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''

### 2018-10-17 reports/preprint.tex
after toms changes

For each lipid, the tail layer thickness, $d_t$, increases with chain length and in general agrees with the literature for monolayers on water\cite{Mohwald1990,Vaknin1991}:
For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
In all cases the surface roughness was found to be relatively high compared to water. This is expected because the absolute surface tension of the DES is less than water\cite{Arnold2015}.

>>>>

For each lipid, the tail layer thickness, $d_t$, increases with chain length and in general agrees with the literature for monolayers on water\cite{Mohwald1990,Vaknin1991}:
For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
In all cases the surface roughness was found to be relatively high compared to water.
This is expected because the absolute surface tension of the DES is less than water, while a previous XRR measurement of pure choline chloride:glycerol suggests a roughness of 3.3\si{\angstrom}\cite{Arnold2015}, significantly higher than the capillary wave roughness of water of about 2.8\si{\angstrom}.

### 2018-10-17 reports/si.tex
after toms changes

\section{Methods}
XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\eV} photon energy using the double-crystal-deflector\cite{Arnold2012} and a Pilatus 100k detector. The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\AA^{-1}}. The data were normalised with respect to the incident beam and the background was measured from off-specular region-of-interest and subsequently subtracted. Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase. XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius} under a Helium atmosphere. The aluminium Wilhelmy plate was used over a traditional paper plate because the DES was found to wet Aluminium but not paper, and therefore allowed more reproducible surface pressure measurements.
It is noted that the known phase transitions of DMPC and DMPG are 24 and \SI{23}{\celsius} respectively, which is very close to our measurement temperature. For the sake of our assumptions during analysis it is therefore important that we were able to to determine which phase (LE or LC) the molecules are in. This was done directly using Grazing incident X-ray diffraction (see below).

>>>>

\section{Methods}
XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\eV} photon energy using the double-crystal-deflector\cite{Arnold2012} and a Pilatus 100k detector. The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\AA^{-1}}. The data were normalised with respect to the incident beam and the background was measured from off-specular region-of-interest and subsequently subtracted. Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase. XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an Aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius} under a Helium atmosphere. The Aluminium Wilhelmy plate was used over a traditional paper plate because the DES was found to wet Aluminium but not paper, and therefore allowed more reproducible surface pressure measurements.
It is noted that the known phase transitions of DMPC and DMPG are 24 and \SI{23}{\celsius} respectively, which is very close to our measurement temperature. For the sake of our assumptions during analysis it is therefore important that we were able to to determine which phase (LE or LC) the molecules are in. This was done directly using Grazing incident X-ray diffraction (see below).
